---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE
)
```

# parable

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of parable is to enable the user to use `fable` in parallel.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("markfairbanks/parable")
```

Note that `parable` uses a custom version of `fabletools`, which can be installed here:

``` r
# install.packages("devtools")
devtools::install_github("markfairbanks/fabletools")
```

## Functions

`parable` has 3 core functions:

* `parallel_model()`
* `parallel_forecast()`
* `parallel_accuracy()`

Each function is used just like the functions from `fable`, but a `future::plan` must be set.

We start with an example tsibble with 50 time-series.

```{r}
pacman::p_load(tidyverse, parable, janitor, lubridate,
               tsibble, fable, fabletools, feasts, tsibbledata)

aus_ts <- tsibbledata::aus_retail %>%
  rename_all(janitor::make_clean_names) %>%
  update_tsibble(key = series_id, index = month) %>%
  select(-state, -industry) %>%
  filter(year(month) >= 2010) %>%
  group_by_key() %>%
  filter(group_indices() <= 50) %>%
  ungroup()

aus_ts
```

The below chunk shows how to use `parable`, with `tictoc` used to show the timing of the `parallel_model()` step:

```{r warn = FALSE}
pacman::p_load(future)

plan(multiprocess, workers = 5)

tictoc::tic()

parable_mbl <- aus_ts %>%
  parallel_model(ets = ETS(turnover))

tictoc::toc()
```

Which we can then compare to the timing of normal `fable`:

```{r}
tictoc::tic()

fable_mbl <- aus_ts %>%
  model(ets = ETS(turnover))

tictoc::toc()
```


